---
title: "Research Rough Simulation"
output: pdf_document
date: "2023-08-01"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Experiment Setting

Assume large proportion of observations are from heavy users, smaller from light users. In response, light users are assumed to have greater variance, because their usage patterns are not well established due to being new to the product, hence there is more randomness in their activity. 

With randomization, there are basically the same proportion of light and heavy users in each treatment and control groups. 

Heavy users have some pre-experimental data, light users do not. 

```{r}
set.seed(1)

# set params
heavy_mu = 100
heavy_sd = 20
heavy_prop = 0.80
light_mu = 80
light_sd = 50
light_prop = 1 - heavy_prop
n = 100
mean_t_effect = 5

# generate responses for light and heavy users
heavy_exp = rnorm(round(n * heavy_prop), heavy_mu, heavy_sd) 
light_exp = rnorm(round(n * light_prop), light_mu, light_sd)
combined_exp = c(heavy_exp, light_exp)

b = min(combined_exp) - 1
e = max(combined_exp) + 1

ax = round(seq(b, e, length.out = n / 4))

# plot distributions
hist(combined_exp, breaks = ax, col = rgb(1,0,0,0.25))
hist(heavy_exp, breaks = ax, col = rgb(0,1,0,0.25))
hist(light_exp, breaks = ax, col = rgb(0,0,1,0.25))

# randomly assign treatments, treatment effects are assumed to be mostly positive with small variance
group_size = round(length(combined_exp) / 2)
t_assign = sample(1:length(combined_exp), group_size)
t_effect = rnorm(group_size, mean_t_effect, 2)
treatment = combined_exp[t_assign] + t_effect
control = combined_exp[-t_assign]
post_treat_ax = round(seq(min(c(treatment, control))-1, max(c(treatment, control))+1, length.out = n / 4))

# plot treatment response vs control response
hist(treatment, breaks = post_treat_ax, col = rgb(1,1,0,0.25))
hist(control, breaks = post_treat_ax, add = TRUE, col = rgb(1,0,1,0.25))
t = t.test(treatment, control)
t
power.t.test(group_size, mean(treatment) - mean(control), sd = t$stderr, sig.level = 0.05, type = "two.sample", alternative = "two.sided")
```
```{r}
set.seed(1)
# test with just heavy users
group_size = round(length(heavy_exp) / 2)
t_assign = sample(1:length(heavy_exp), group_size)
t_effect = rnorm(group_size, mean_t_effect, 2)
treatment = heavy_exp[t_assign] + t_effect
control = heavy_exp[-t_assign]
post_treat_ax = round(seq(min(c(treatment, control))-1, max(c(treatment, control))+1, length.out = n / 4))

# plot treatment response vs control response
hist(treatment, breaks = post_treat_ax, col = rgb(1,1,0,0.25))
hist(control, breaks = post_treat_ax, add = TRUE, col = rgb(1,0,1,0.25))
t = t.test(treatment, control)
t
power.t.test(group_size, mean(treatment) - mean(control), sd = t$stderr, sig.level = 0.05, type = "two.sample", alternative = "two.sided")
```

```{r}
set.seed(1)
# test with just heavy users
group_size = round(length(light_exp) / 2)
t_assign = sample(1:length(light_exp), group_size)
t_effect = rnorm(group_size, mean_t_effect, 2)
treatment = heavy_exp[t_assign] + t_effect
control = heavy_exp[-t_assign]
post_treat_ax = round(seq(min(c(treatment, control))-1, max(c(treatment, control))+1, length.out = n / 4))

# plot treatment response vs control response
hist(treatment, breaks = post_treat_ax, col = rgb(1,1,0,0.25))
hist(control, breaks = post_treat_ax, add = TRUE, col = rgb(1,0,1,0.25))
t = t.test(treatment, control)
t
power.t.test(group_size, mean(treatment) - mean(control), sd = t$stderr, sig.level = 0.05, type = "two.sample", alternative = "two.sided")
```

```{r}
set.seed(1)
# pre-experimental data for heavy users
# how to reduce correlation? its unrealistically high. need more noise 
heavy_pre = heavy_exp + rexp(length(heavy_exp), 1/10)*runif(length(heavy_exp), -1,1)
theta = cov(heavy_exp, heavy_pre)/var(heavy_pre)
heavy_cuped = heavy_exp - theta * heavy_pre + theta * mean(heavy_pre)

# test with just heavy users applying cuped
gp = heavy_cuped
group_size = round(length(gp) / 2)
t_assign = sample(1:length(gp), group_size)
t_effect = rnorm(group_size, mean_t_effect, 2)
treatment = gp[t_assign] + t_effect
control = gp[-t_assign]
post_treat_ax = round(seq(min(c(treatment, control))-1, max(c(treatment, control))+1, length.out = 10))

# plot treatment response vs control response
hist(treatment, breaks = post_treat_ax, col = rgb(1,1,0,0.25), ylim = c(0,0.5))
hist(control, breaks = post_treat_ax, add = TRUE, col = rgb(1,0,1,0.25), ylim = c(0, 0.5))
legend("topright", c("treatment", "control"), fill=c(rgb(1,1,0,0.25), rgb(1,0,1,0.25)))
t = t.test(treatment, control)
t
power.t.test(group_size, mean(treatment) - mean(control), sd = t$stderr, sig.level = 0.05, type = "two.sample", alternative = "two.sided")
```